
%-------------------------
% Resume in Latex
% Author : Shubham Bajpai
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}


\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/bajpai-shubham/}{\huge Shubham Bajpai}}\\
  \href{https://www.linkedin.com/in/bajpai-shubham/}{www.linkedin.com/in/bajpai-shubham/} & Email : \href{mailto:shubhambajpai1994@gmail.com}{shubhambajpai1994@gmail.com}\\
  \href{https://github.com/shubhambajpai1994}{www.github.com/shubhambajpai1994} & Mobile : +91-8109217716 \\
\end{tabular*}



%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {International Institute of Information Technology, Bangalore}{}
      {Master of Technology in Information Technology | CGPA: 3.28/4}{July 2017 -- July 2019}
    \resumeSubheading
      {Shri Shankaracharya Group Of Institutions, Bhilai}{}
      {Bachelor of Engineering in Computer Science and Engineering | CGPA: 8.09/10}{Aug. 2013 -- July 2017}
    \resumeSubheading
      {Holy Cross Sen. Sec. School, Kapa, Raipur}{}
      {12\textsuperscript{th} Grade | 72.2\%}{2012}
    \resumeSubheading
      {Holy Cross Sen. Sec. School, Kapa, Raipur}{}
      {10\textsuperscript{}{th} Grade | CGPA: 8.2/10}{2010}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {ClearTax}{Bangalore, India}
      {Software Engineering Intern}{May 2018 - Present}
      \resumeItemListStart
        \resumeItem{MarketPlace}
          {Working as a back-end engineer in the MarketPlace team of ClearTax. Contributing to various feature additions and bug fixes.}
        \resumeItem{Fulfillment-Backend}
          {My work included developing new features like credit note service,  leads services,  adding reminder feature for follow up, report cron jobs service and many more along-with handling on call issues related to orders in marketplace.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------SKILLS------------------
\section{Skills and Abilities}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}
      { C++, Java, Python}
      \resumeSubItem{Query Languages}
      { SQL, CQL, HQL}
    \resumeSubItem{Tools, Libraries and Frameworks}
      {Net Beans, Eclipse, Gurobi, PyCharm, Scikit, Intellij IDEA, Drop Wizard,Hibernate, Maven, GurobiPy}
    \resumeSubItem{Areas of Interest}
      {Algorithms, Optimization, Machine Learning, Geographic Information Systems}
  \resumeSubHeadingListEnd
  
  
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Indian Railways Route Optimization and Scheduling }
      {The objective of the project was to find a conflict free schedule for a set of trains in a given railway network satisfying some constraints. We deal with large scale railway network at the scale of Indian Railways. Indian Railways poses a computational challenge for finding an optimal schedule. We developed algorithm with capability to deal with a fraction of the overall requirement with the improvement of a block section.}
    \resumeSubItem{User Engagement}
      {Developed a model for classification of users based on their visiting pattern and activities on the platform and send relevant nudges to boost user engagement on platform. Designed a custom classification algorithm with the improvement over other standard algorithms.}
    \resumeSubItem{Programming Language Skroth and Interpreter Valyria}
      { Developed an experimental programming language inspired by ”Game Of Thrones”and the syntax derived from quotes and phrases of the book series ”The Song of Ice and Fire”.}
    \resumeSubItem{Crime Based Grading and Mapping Safe Zones}
      {Developed a GIS based application capable of finding safe zones geographically based on previous crime data of a region and plotting a safety level map so as to classify unsafe zones and safe zones in a city.}
  \resumeSubHeadingListEnd


%----------ACHIEVEMENTS--------------
\section{Achievements}
\resumeSubHeadingListStart
    \itemsep-0.25em 
    \item Secured \textbf{AIR 36} All India Rank in \textbf{JEST 2017}.
    \item Secured \textbf{AIR 1087} in \textbf{GATE 2018}.
    \item Secured \textbf{AIR 937} in \textbf{GATE 2017}.
    \item Secured \textbf{AIR 753} in \textbf{CodeVita 2016}.
    \item Hackerrank rank 2692\textsuperscript{*} and \textbf{96 percentile O(logn)} in algorithms.
    \item Event Head\emph{(Technical)} of techno-cultural fest Samvid 2016.
    \item Secured 1st Rank n zonal Robotics Competition 2013 held in association with IISC Bengaluru.
    \item Secured \textbf{517} in \textbf{CGPET 2013}.
    \item Secured \textbf{1010} in \textbf{CGPET 2012}.
    
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
© 2018 GitHub, Inc.
Terms
Privacy
Security
Status
Help
Contact GitHub
API
Training
Shop
Blog
About
Press h to open a hovercard with more details.
